Extreme Value Chapter

### 2022-02-28 Ch3_samplesize/Figures_Ch3.Rmd
Bias figure ready

>>>>

```{r eval = FALSE, fig.width=8, fig.height=4}

# See it compared to the original theta
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize) +
  scale_color_manual(values = pal_sampsize) +
  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "Simple Lomax") +
  theme_bw() +
  theme(legend.position = "none") -> a

nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  ggplot(., aes(x = thresh_tests, y = log_St_hat2 - log(theta), fill = samp_n_tests, color = samp_n_tests)) +
  # facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot(alpha = 0.9) +
  geom_hline(yintercept = 0, color = "red") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Long-distance level", y = "log(theta_hat) - log(theta)", title = "GLM Lomax") +
  theme_bw() +
  theme(legend.position = "right") -> b

# Figure 3
Introduce the numerical estimation thing with the simple lomax:

```{r fig.width=7, fig.height=4}
nreps_mles_df %>% 
  ggplot()+
  geom_point(aes(x = alpha_star, y = k_star, color = "Simple Lomax"), size = 4, alpha = 0.5) +
  geom_point(aes(x = alpha_glm, y = k_glm, color = "Lomax GLM"), size = 4, alpha = 0.5) +
  scale_y_log10() +
  scale_x_log10() +
  scale_color_manual(values = c("grey20", "dodgerblue4"), name = "") +
  labs(x = "Log(alpha)", y = "Log(k)") +
  theme_bw() +
  theme(legend.position = "bottom") -> a

nreps_mles_df %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>% 
  ggplot()+
  facet_wrap(~labelsamp) +
  geom_point(aes(x = alpha_star, y = k_star, color = "Simple Lomax"), size = 4, alpha = 0.5) +
  geom_point(aes(x = alpha_glm, y = k_glm, color = "Lomax GLM"), size = 4, alpha = 0.5) +
  scale_y_log10() +
  scale_x_log10() +
  scale_color_manual(values = c("grey20", "dodgerblue4"), name = "") +
  labs(x = "Log(alpha)", y = "Log(k)") +
  theme_bw() +
  theme(legend.position = "none",
        axis.text = element_blank()) -> b

ableg <- get_legend(a)

top <- plot_grid(a + theme(legend.position = "none"), b, ncol = 2)

plot_grid(top, ableg, nrow = 2, rel_heights = c(1, 0.1))

# Figure 4

Do MSE? or bias to show that the are biased estimators:

```{r fig.height=3, fig.width=7}
nreps_mles_df %>% 
  mutate(samp_n_tests = factor(samp_n_tests),
         thresh_tests = factor(thresh_tests)) %>% 
  group_by(thresh_tests, samp_n_tests) %>% 
  summarize(Eval_theta_hat = mean(log_St_hat2),
            theta = mean(theta),
            bias = Eval_theta_hat - theta) %>% 
  ggplot(., aes(y = bias, x = thresh_tests)) +
  geom_jitter(aes(color = samp_n_tests), size = 3, alpha = 0.9, width = 0.1) +
  geom_hline(yintercept = 0, color = "red") +
  scale_color_manual(values = pal_sampsize, name = "Sample Size") +
  labs(x = "Long-distance level", y = "Bias", title = "GLM Lomax") +
  theme_bw()
